A contrast of meta and metafor packages for meta-analyses in R

### 2020-06-30 ms/2020/ms.Rmd
appendices listed.
setup

---
title: "A contrast of meta and metafor packages for meta-analyses in R"
output: pdf_document
bibliography: references.bib
---

@@

>>>>

---
title: "A contrast of meta and metafor packages for meta-analyses in R"
output:
  word_document: default
  pdf_document: default
bibliography: references.bib
---

@@

### Appendix A. A list of objects included in each package when loaded into the R environment.

### Appendix B. A contrast of analyses done using the R packages meta and metafor.

### Appendix C. An example of a meta-analysis conducted in Stata 16.
